---
title: "Run RBEROST"
date: "5/6/2021"
date (updated): "8/4/2025"
output: html_document
---

## Configure R

This code will load the required R packages that RBEROST uses. To run the code, click the green triangle below. If no green arrow appears, and instead there is a red square, click the red square to stop any ongoing processes and a green triangle should appear in its place. When clicked, the green triangle will turn into a red square until the code is finished.

**Important:** Please open this project by double-clicking `Tier_1_Optimization-SSWR_5_3_2.Rproj` to ensure proper package management via renv.

```{r configureR}
# Load required packages
# Check if renv is active (it should be if you opened via the .Rproj file)
if (!identical(Sys.getenv("RENV_PROJECT"), normalizePath("../..", winslash = "/"))) {
  cat("\n=======================================================================\n")
  cat("WARNING: renv is not active!\n")
  cat("=======================================================================\n")
  cat("For proper package management, please:\n")
  cat("  1. Close this file\n")
  cat("  2. Open 'Tier_1_Optimization-SSWR_5_3_2.Rproj' in the project root\n")
  cat("  3. This will automatically activate renv and load correct packages\n")
  cat("  4. Then reopen this RMarkdown file\n")
  cat("=======================================================================\n\n")
}

# If packages are missing after opening via .Rproj, run: renv::restore()

library(tidyverse)
library(reshape2)
library(data.table)
library(stringr)
library(foreach)
library(shiny)
library(shinycssloaders)
library(tidygraph)
library(bit64)
library(beepr)

# Alternative: Use pacman for backward compatibility (if preferred)
# Note: pacman will use the renv-managed packages
# pacman::p_load("tidyverse", "reshape2", "data.table", "stringr", "foreach", 
#                "shiny", "shinycssloaders", "tidygraph", "bit64", "beepr")
```

## Run Batch Preprocessor

To run the preprocessor, change any lines of code necessary and click the green triangle below. If no green arrow appears, and instead there is a red square, click the red square to stop any ongoing processes and a green triangle should appear in its place. When clicked, the green triangle will turn into a red square until the code is finished.

```{r runpreprocessor, warning = FALSE}

#
#
#
### Set file paths and required file names ###############################################################################################

# This variable represents the working directory where RBEROST is located. You will need to write out the full path to your RBEROST inputs.
working_dir <- "./"

# This variable represents the location of input data files used to develop AMPL model files. If you opened RBEROST through the Tier_1_Optimization-SSWR_5_3_2.Rproj file, the '.' represents the folder where the Tier_1_Optimization-SSWR_5_3_2.Rproj file is located. If you did not open this file through the R project you may need to write out the full path to your RBEROST inputs.
InPath<-paste0(working_dir,"RBEROST-Northeast/Preprocessing/Inputs/")

# This variable represents the location where AMPL model files will be printed for use on the NEOS server. If you opened RBEROST through the Tier_1_Optimization-SSWR_5_3_2.Rproj file, the '.' represents the folder where the Tier_1_Optimization-SSWR_5_3_2.Rproj file is located. If you did not open this file through the R project you may need to write out the full path to your RBEROST inputs.
OutPath<-paste0(working_dir,"RBEROST-Northeast/Preprocessing/Outputs/")

# Define the name of the UserSpecs input file. This file contains the user specifications for the optimization, including the BMPs that will be considered in the optimization. If you wish to change which BMPs are considered, you can edit this file.
user_specs_name <- "01_UserSpecs_BMPs_wCS_NoSeptic.csv" # 01_UserSpecs_BMPs_wCS_NoSeptic.csv

### User Interface ###############################################################################################
MODE <- "Select"
# Mode Options
# "All" will run all watersheds in Long Island Sound
# "Select" will only run select watersheds singled out in the watershed_choices vector

# Select years to include in the model
model_years <- c("01") #, "02"
# Note: years are available from 00 to 20; formatted as "02", "03", ...

# This variable represents the planning horizon in terms of years. Default is 15.
horizon <- 15

# This variable represents to expected interest rate. Default is 0.03, or 3%.
interest_rate <- 0.03
# Load parameter specification
actionable_load <- TRUE # If TRUE, the model will exclude "other" loads from sources such as snowmelt and atmospheric deposition for which there are no applicable BMPs that can reduce them
# Note: Setting to FALSE is much more likely to result in infeasible results since "other" loads typically make up sizeable portions of overall loadings within a watershed, and as such the reduction target percentages exceed the amount that can be reduced by BMPs in other categories. 

# This variable lets the user decide if they wish to consider agricultural BMP efficiencies of practices versus "No Practice" (a default of no conservation practices) or "Baseline" (a default of practices currently in place, and implementing a BMP will remove practices currently in place).
AgBMPcomparison <- "No Practice"

# This variable decides if you will run RBEROST with or without uncertainty. It can be TRUE or FALSE. Running with uncertainty takes longer than running without.
IncludeUncertainty <- FALSE

# If running RBEROST with uncertainty, how many scenarios would you like to view? Default is 3.
n.scenarios <- 3 

# If running RBEROST with uncertainty, how different would you like the scenarios to be? Each scenario will be solved for loading limits that are a certain percentage lower than the previous. Default is 0.01, or 1%.
scenariostepchange <- 0.01


### BMP Specifications

# -------------General notes-------------

# 1. User must specify which BMPs will be considered in the optimization by specifying "X" in the BMP_Selection field of "UserSpecs_BMPs.csv"
# 2. Current input data refers to Northeastern Regional SPARROW loading data and land use data specific to Vermont and New Hampshire
# 3. If more advanced R users would like to assess different locations/data, they would need to search for and update lines of code in the preprocessing code that end in "#*#" 
# Science base reference: https://www.sciencebase.gov/catalog/item/5d4192aee4b01d82ce8da477

# NEOS configuration
email <- "56407@icf.com"
NEOSresults <- "RBEROST-Northeast/Preprocessing/Outputs/Batch Results/"
comments <- "Batch watershed optimization run."

# Define all available watersheds
all_watersheds <- c(
    "Bantam Lake",
    "Batterson Park Pond",
    "Linsley Pond Cedar Pond",
    "Byram River",
    "Farm River",
    "Little Narragansett Bay",
    "Lower Connecticut River",
    "Lower Middle Connecticut River",
    "Mystic Harbor",
    "New Haven Harbor",
    "Niantic Bay",
    "Norwalk Harbor",
    "Pequonnock River",
    "Saugatuck Estuary",
    "Southport Harbor Sasco Brook",
    "Stonington Harbor",
    "Thames River",
    "Upper Connecticut River",
    "Upper Middle Connecticut River"
     # The following watersheds are known to cause errors
     # The majority of the following watersheds have been identified as problematic due to a lack of data in the SPARROW dataset.
     # "Housatonic River",
     # "Kenosia Lake",
)

# Watersheds to exclude (known to cause errors)
exclude_watersheds <- c(
)

setwd(working_dir) # "../"
source("./RBEROST-Northeast/R/03_BatchRBEROSTRun-Northeast_V1.R")
```

## Run Postprocessor

To run the postprocessor, click the green triangle below. A window will pop up either in RStudio or in your default web browser. If no green arrow appears, and instead there is a red square, click the red square to stop any ongoing processes and a green triangle should appear in its place. When clicked, the green triangle will turn into a red square until the code is finished. Be aware that simply closing the browser window will not stop the Shiny app. You must also click the red square below if you wish to relaunch the app.

```{r runpostprocessor}
# Increase the max file size to accomodate dynamic SPARROW
options(shiny.maxRequestSize = 100000 * 1024^2)
setwd(working_dir) # "../"
source("./RBEROST-Northeast/R/02_Optimization_RunShiny-Northeast.R", local = TRUE)
```
