---
title: "Local Sensitivity Analysis"
author: "Cathy Chamberlin, Sam Ennett"
date: "11/04/2025"
output: html_document
---

## Setup
```{r}
if (!require(pacman)) install.packages("pacman")
pacman::p_load(
    data.table, tidyverse, foreach, rneos, doParallel, RColorBrewer, shiny, magrittr, dplyr, purrr, stringr, ggplot2, readr, tzdb
)
theme_set(theme_classic())
registerDoParallel()
```

## Define functions
```{r}
my_savematch <- function(x, set, include = TRUE) {
  if(include == TRUE) {
    tmp <- x[which(x %in% set)]
  } else if(include == FALSE) {
    tmp <- x[which(!(x %in% set))]
  }
  
  return(tmp)
}

options(RCurlOptions = list(ssl.verifypeer = FALSE))

my_NgetSolverTemplate <- function (
  category, solvername, inputMethod, nc = CreateNeosComm()
) {
  if (!(class(nc) == "NeosComm")) {
    stop("\nObject provided for 'nc' must be of class 'NeosComm'.\n")
  }
  
  call <- match.call()
  
  ans <- xml.rpc(
    url = nc@url, 
    method = "getSolverTemplate", 
    .args = list(
      category = category, solvername = solvername, inputMethod = inputMethod
    ), 
    .convert = TRUE, 
    .opts = nc@curlopts, 
    .curl = nc@curlhandle
  )
  
  email.xmlcode <- "\n\n<email><![CDATA[...Insert Value Here...]]></email>"
  
  ans_rev <- if(
    grepl("email", ans)
  ) {
    ans
  } else {
    paste0(
      substr(ans, 1, nchar(ans)-13), 
      email.xmlcode, 
      substr(ans, (nchar(ans)-13), nchar(ans))
    )
  }
  
  xml <- xmlRoot(xmlTreeParse(ans_rev, asText = TRUE))
  
  res <- new("NeosXml", xml = xml, method = "getSolverTemplate",
             call = call, nc = nc)
  
  return(res)
}

read_csvs_using_baseR <- function(path) {
  tryCatch(
    # when reading semicolon separated files, having a comma separator causes `read.csv` to error. Using read.csv2 causes no error.
    expr = {
      dt <- data.table::fread(
        file = path, 
        colClasses = "character",
        header = FALSE,
        blank.lines.skip = FALSE,
        sep = "\n"
      )
      return(dt)
    },
    error = function(e) {stop(safeError(error = e))} # return a safeError if a parsing error occurs
  )
}
```

## Set Filepath locations
### AMPL scripts
The AMPL scripts folder will be the location where the AMPL model files for each scenario will be written. 
You will also need to paste the AMPL files for the RBEROST model you wish to analyze the sensitivity of into this folder. These files will come from the pre-processing code outputs folder.

### NEOS results
This folder will be where the results from NEOS are saved. This analysis will generate a large number of files, so it is recommended to have a dedicated folder for these results.

### Figure outputs
This folder will be where the figures generated from the sensitivity analysis are saved.

```{r set filepaths}
AMPLscriptsfolder <- "./RBEROST-Northeast/SensitivityAnalysis/AMPLscripts/Pequonnock River/"
NEOSresults <- "./RBEROST-Northeast/SensitivityAnalysis/NEOSResults/Pequonnock River/"
figureoutputs <- "./RBEROST-Northeast/SensitivityAnalysis/Images/Pequonnock River/"
```

## Load AMPL Model
```{r}
AMPLmod <- read_csvs_using_baseR(
  paste0(AMPLscriptsfolder, "STmodel_seasonal.mod")
) %>% rename(X = 1)
```


## List all parameters to work with
This chunk of code creates a table with all the parameters used in the model, and the sets that they are iterated over. 
Sets of comids are omitted, as we are going to assume changes to parameters occur uniformly across the watershed. 

```{r}
## list the sets that we are using for the sensitivity analysis
## Sets of comids are omitted. There are thousands of them, so we will make the assumption that changes to parameters are uniform across the watershed. 
set_lines <- AMPLmod[which(sapply(AMPLmod, grepl, pattern = "set"))]
sets <- unlist(
  lapply(
    lapply(
      lapply(
        str_extract_all(set_lines, pattern = "(?<=set ).+?(?= :=)")[[1]], 
        str_split_fixed, 
        pattern = "within", 
        n = 2
      ), 
      "[[", 
      1
    ), 
    gsub, 
    pattern = " ", 
    replacement = ""
  )
)

sets_toiterateover <- sets[which(!grepl("comid", sets))]
sets_nottoiterateover <- sets[which(grepl("comid", sets))]
## get members of the sets
set_definition_lines <- AMPLmod[
  which(sapply(AMPLmod, grepl, pattern = "set")) + 1
]

set_definitions <- lapply(set_definition_lines, str_extract_all, pattern = "(?<=\\{).+?(?=\\})")
set_members_toiterateover <- set_definitions$X[which(sets %in% sets_toiterateover)]

## list the parameters
## We will not do sensitivity analysis on acftoft3, pcp or agBMP_minarea, because these are not variable and there is little to no uncertainty in the numbers. We will not do uncertainty analysis on ps_coef, urban_coef, ag_coef or ripbuf_coef, because these are created from other parameters, and we will already be doing uncertainty analysis on those other parameters.
params <- AMPLmod[which(sapply(AMPLmod, grepl, pattern = "param"))] %>%
  mutate(
    param_name = str_split_fixed(X, pattern = " ", n = 3)[,2],
    param_sets = str_extract_all(X, pattern = "(?<=\\{).+?(?=\\})")
  ) %>%
  filter(
    !param_name %in% c(
      "acfttoft3", 
      "pcp", 
      "agBMP_minarea;", 
      "ps_coef", 
      "urban_coef",
      "ag_coef", 
      "ripbuf_coef"
    )
  )

## create a table of parameters and the sets to iterate over that we need to test for sensitivity
params_totest <- foreach(i = 1:nrow(params), .combine = "rbind") %do% {
  
  param <- params$param_name[i]
  
  if(length(params$param_sets[i][[1]]) > 0) {
    if(grepl(x = params$param_sets[i][[1]], pattern = "comid")) {
      if(grepl(x = params$param_sets[i][[1]], pattern = ",")) {
        
        param_sets <- unlist(
          lapply(
            unlist(
              lapply(
                lapply(
                  str_split(unlist(params$param_sets[i]), pattern = ","), 
                  gsub, 
                  pattern ="[a-z] in ", 
                  replacement = ""
                )[[1]], 
                gsub, 
                pattern = " ", 
                replacement = ""
              )
            ), 
            my_savematch, 
            set = sets_toiterateover
          )
        )
        
        param_comidsets <- unlist(
          lapply(
            unlist(
              lapply(
                lapply(
                  str_split(unlist(params$param_sets[i]), pattern = ","), 
                  gsub, 
                  pattern ="[a-z] in ", 
                  replacement = ""
                )[[1]], 
                gsub, 
                pattern = " ", 
                replacement = ""
              )
            ), 
            my_savematch, 
            set = sets_nottoiterateover
          )
        )
        
        # Fix for seasonal model: map comid_N1 to comid_all_N and comid_P1 to comid_all_P
        if(length(param_comidsets) > 0) {
          param_comidsets <- gsub("comid_N1", "comid_all_N", param_comidsets)
          param_comidsets <- gsub("comid_P1", "comid_all_P", param_comidsets)
        }
      } else {
        param_sets <- NA_character_
        
        param_comidsets <- unlist(
          lapply(
            unlist(
              lapply(
                lapply(
                  str_split(unlist(params$param_sets[i]), pattern = ","), 
                  gsub, 
                  pattern ="[a-z] in ", 
                  replacement = ""
                )[[1]], 
                gsub, 
                pattern = " ", 
                replacement = ""
              )
            ), 
            my_savematch, 
            set = sets_nottoiterateover
          )
        )
        
        # Fix for seasonal model: map comid_N1 to comid_all_N and comid_P1 to comid_all_P
        if(length(param_comidsets) > 0) {
          param_comidsets <- gsub("comid_N1", "comid_all_N", param_comidsets)
          param_comidsets <- gsub("comid_P1", "comid_all_P", param_comidsets)
        }
      }
    } else {
      param_sets <- unlist(
        lapply(
          unlist(
            lapply(
              lapply(
                str_split(unlist(params$param_sets[i]), pattern = ","), 
                gsub, 
                pattern ="[a-z] in ", 
                replacement = ""
              )[[1]], 
              gsub, 
              pattern = " ", 
              replacement = ""
            )
          ), 
          my_savematch, 
          set = sets_toiterateover
        )
      )
      
      param_comidsets <- NA_character_
    }
  } else {
    param_sets <- NA_character_
    param_comidsets <- NA_character_
  }
  
  
  if(length(param_sets) > 0 && !any(is.na(param_sets))) {
    params_totest_tmp <- foreach(j = 1:length(param_sets), .combine = "rbind")  %do% {
      
      param_set <- param_sets[j]
      
      param_othersets <- if(length(param_sets) > 1) {
        param_sets[-j]
      } else {NA_character_}
      
      param_set_members_unformatted <- set_members_toiterateover[
        which(sets_toiterateover == param_set)
      ][[1]]
      
      param_set_members_extracted <- str_extract_all(
        param_set_members_unformatted, pattern = "(?<=\\').+?(?=\\')"
      )
      
      # Check if any matches were found
      if(length(param_set_members_extracted) > 0 && length(param_set_members_extracted[[1]]) > 0) {
        param_set_members <- param_set_members_extracted[[1]]
        
        param_set_members_dat <- param_set_members[
          which(param_set_members != ", ")
        ]
        
        data.frame(
          param = rep(param, length(param_set_members_dat)),
          sets = rep(param_set, length(param_set_members_dat)),
          member = param_set_members_dat,
          comidsets = rep(if(length(param_comidsets) > 0 && !any(is.na(param_comidsets))) paste(param_comidsets, collapse = ",") else NA_character_, length(param_set_members_dat)),
          othersets = rep(if(length(param_othersets) > 0 && !any(is.na(param_othersets))) paste(param_othersets, collapse = ",") else NA_character_, length(param_set_members_dat))
        )
      } else {
        # Return NULL for this iteration if no matches found
        NULL
      }
    }
  } else if (length(param_comidsets) > 0 && !any(is.na(param_comidsets))){
    
    params_totest_tmp <- data.frame(
      param = param,
      sets = NA_character_,
      member = NA_character_,
      comidsets = if(length(param_comidsets) > 0 && !any(is.na(param_comidsets))) paste(param_comidsets, collapse = ",") else NA_character_,
      othersets = NA_character_
    )
    
  } else {
    params_totest_tmp <- data.frame(
      param = param,
      sets = NA_character_,
      member = NA_character_,
      comidsets = NA_character_,
      othersets = NA_character_
    )
  }
  params_totest_tmp
}
params_totest_dat <- params_totest %>% filter(member != "," | is.na(member))
```

## System Status Check and Cleanup

```{r system status check}
# Function to validate result file (moved here for early availability)
validate_result_file <- function(filepath, required_patterns = c("cost =", "solve_result")) {
  if (!file.exists(filepath)) {
    return(FALSE)
  }
  
  tryCatch({
    content <- readLines(filepath, warn = FALSE)
    content_text <- paste(content, collapse = "\n")
    
    # Check for required patterns
    for (pattern in required_patterns) {
      if (!grepl(pattern, content_text)) {
        return(FALSE)
      }
    }
    
    # Check file is not empty or too small
    if (length(content) < 5) {
      return(FALSE)
    }
    
    # Check for infeasible solve_result
    solve_result_match <- regmatches(content_text, regexpr("solve_result\\s*=\\s*\\w+", content_text))
    if (length(solve_result_match) > 0) {
      solve_result_value <- gsub(".*=\\s*", "", solve_result_match)
      if (grepl("infeasible", solve_result_value, ignore.case = TRUE)) {
        return(FALSE)  # Mark as invalid if infeasible
      }
    }
    
    return(TRUE)
  }, error = function(e) {
    return(FALSE)
  })
}

# Check if necessary directories exist
if (!dir.exists(AMPLscriptsfolder)) {
  dir.create(AMPLscriptsfolder, recursive = TRUE)
  cat("Created AMPL scripts directory:", AMPLscriptsfolder, "\n")
}

if (!dir.exists(NEOSresults)) {
  dir.create(NEOSresults, recursive = TRUE)
  cat("Created NEOS results directory:", NEOSresults, "\n")
}

# Check existing result files
existing_files <- list.files(NEOSresults, pattern = "NEOSresult_.*\\.txt", full.names = TRUE)

if (length(existing_files) > 0) {
  cat("Found", length(existing_files), "existing result files.\n")
  
  # Validate existing files
  valid_files <- sapply(existing_files, function(f) {
    if (grepl("_reference", f)) {
      validate_result_file(f, c("cost =", "solve_result"))
    } else {
      validate_result_file(f, c("cost =", "solve_result", "frac ="))
    }
  })
  
  invalid_files <- existing_files[!valid_files]
  
  if (length(invalid_files) > 0) {
    cat("Found", length(invalid_files), "invalid/corrupted result files (missing required fields):\n")
    for (f in invalid_files) {
      cat(" -", basename(f), "\n")
    }
    
    # Option to clean up corrupted files (only those missing required fields)
    cleanup_response <- readline(prompt = "Remove files with missing required fields? (y/n): ")
    if (tolower(cleanup_response) == "y") {
      file.remove(invalid_files)
      cat("Removed", length(invalid_files), "corrupted files.\n")
    }
  } else {
    cat("All existing result files have required fields.\n")
  }
  
  # Report on infeasible solutions separately (for info only)
  infeasible_count <- 0
  for (f in existing_files[valid_files]) {
    content <- paste(readLines(f, warn = FALSE), collapse = "\n")
    if (grepl("solve_result\\s*=\\s*infeasible", content, ignore.case = TRUE)) {
      infeasible_count <- infeasible_count + 1
    }
  }
  if (infeasible_count > 0) {
    cat("Note:", infeasible_count, "result files contain infeasible solutions (saved for troubleshooting).\n")
  }
} else {
  cat("No existing result files found. Starting fresh.\n")
}

# Check NEOS connectivity
cat("Testing NEOS connectivity...\n")
tryCatch({
  test_template <- my_NgetSolverTemplate(
    category = "lp", solvername = "CPLEX", inputMethod = "AMPL"
  )
  cat("NEOS connection successful.\n")
}, error = function(e) {
  cat("NEOS connection failed:", e$message, "\n")
  cat("Please check internet connection and NEOS server status.\n")
})

cat("System status check complete.\n\n")
```


## Write AMPL reference script

```{r write reference script}
# -------------Develop command file-------------

cat(
  "#WMOST Optimization Screening Tool AMPL command file
solve;
option display_precision 10;
display solve_result_num, solve_result;
display cost.result;
display cost;

option display_1col 10000000000;
option display_width 100000000000;
option omit_zero_rows 1;
option omit_zero_cols 1;
display seasons;
display years;
display sum {c in comid_all} (ps_coef[c] * point_dec[c]);
display {u in urban_bmp} sum {c in comid_all} (urban_coef[c,u] * urban_frac[c,u]);
display {a in ag_bmp} sum {c in comid_all} (ag_coef[c,a] * ag_frac[c,a]);
display {r in ripbuf_bmp} sum {c in comid_all} (ripbuf_coef[c, r] * ripbuf_length[c, r]);",
file = paste(AMPLscriptsfolder, "STcommand_reference.amp", sep=""),
sep = "\n"
)
```

```{r solve reference model}

# Function to submit NEOS job with retry logic
submit_neos_job_with_retry <- function(argslist, tmp, max_retries = 3, base_delay = 5) {
  
  for (attempt in 1:max_retries) {
    tryCatch({
      cat("Attempt", attempt, "of", max_retries, "\n")
      
      ## create XML string
      xmls <- CreateXmlString(neosxml = tmp, cdatalist = argslist)
      
      ## Submit job
      job.xml.text <- NsubmitJob(
        xmlstring = xmls, user = "rneos", interface = "", id = 0
      )
      
      ## Retrieve results
      resultfile <- NgetFinalResults(obj = job.xml.text, convert = TRUE)
      
      # Validate result content - only check if we got a response
      if (is.null(resultfile@ans) || length(resultfile@ans) == 0) {
        stop("Empty result returned from NEOS")
      }
      
      # Log the solve_result for informational purposes, but don't reject the result
      result_text <- paste(resultfile@ans, collapse = "\n")
      solve_result_match <- regmatches(result_text, regexpr("solve_result\\s*=\\s*\\w+", result_text))
      if (length(solve_result_match) > 0) {
        solve_result_value <- gsub(".*=\\s*", "", solve_result_match)
        if (grepl("infeasible", solve_result_value, ignore.case = TRUE)) {
          cat("Note: NEOS returned infeasible solution. Saving result for troubleshooting.\n")
        }
      }
      
      cat("Job completed on attempt", attempt, "\n")
      return(resultfile)
      
    }, error = function(e) {
      cat("Attempt", attempt, "failed:", e$message, "\n")
      
      if (attempt < max_retries) {
        delay <- base_delay * (2 ^ (attempt - 1)) + runif(1, 0, 2)  # Exponential backoff with jitter
        cat("Waiting", round(delay, 1), "seconds before retry...\n")
        Sys.sleep(delay)
      } else {
        stop("All retry attempts failed. Last error: ", e$message)
      }
    })
  }
}

# Function to validate result file
validate_result_file <- function(filepath, required_patterns = c("cost =", "solve_result")) {
  if (!file.exists(filepath)) {
    return(FALSE)
  }
  
  tryCatch({
    content <- readLines(filepath, warn = FALSE)
    content_text <- paste(content, collapse = "\n")
    
    # Check for required patterns
    for (pattern in required_patterns) {
      if (!grepl(pattern, content_text)) {
        return(FALSE)
      }
    }
    
    # Check file is not empty or too small
    if (length(content) < 5) {
      return(FALSE)
    }
    
    # Do NOT reject files with infeasible solve_result - we want to keep them for troubleshooting
    # Just validate that the file has the expected structure
    
    return(TRUE)
  }, error = function(e) {
    return(FALSE)
  })
}

tmp <-my_NgetSolverTemplate(
  category = "lp", solvername = "CPLEX", inputMethod = "AMPL"
)
## setting path to model and data files
modf <- paste0(AMPLscriptsfolder, "STmodel_seasonal.mod")
datf <- paste0(AMPLscriptsfolder, "STdata_seasonal.dat")
comf <- paste0(AMPLscriptsfolder, "STcommand_reference.amp")

## enter email & comments
email <- "56407@icf.com"

comments <- paste(
  "Reference File for Local sensivity analysis. All BMPs included and no user limits. Default loading targets."
)

## import file contents
modc <- paste(paste(readLines(modf), collapse = "\n"), "\n")
datc <- paste(paste(readLines(datf), collapse = "\n"), "\n")
comc <- paste(paste(readLines(comf), collapse = "\n"), "\n")

## create list object
argslist <- list(
  model = modc, data = datc, commands = comc, comments = comments, email = email
)

# Submit reference job with retry logic
reference_filepath <- paste0(NEOSresults, "NEOSresult_reference.txt")

# Check if valid reference file already exists
if (validate_result_file(reference_filepath)) {
  cat("Valid reference result file already exists. Skipping submission.\n")
} else {
  cat("Submitting reference model to NEOS...\n")
  resultfile <- submit_neos_job_with_retry(argslist, tmp)
  write.table(
    resultfile@ans, file = reference_filepath
  )
  
  # Validate the written file
  if (validate_result_file(reference_filepath)) {
    cat("Reference model completed and file saved.\n")
    # Check if solution was feasible
    content <- paste(readLines(reference_filepath, warn = FALSE), collapse = "\n")
    if (grepl("solve_result\\s*=\\s*infeasible", content, ignore.case = TRUE)) {
      cat("WARNING: Reference model returned infeasible solution. Check model constraints.\n")
    } else {
      cat("Reference model solved successfully.\n")
    }
  } else {
    stop("Reference model result file validation failed (missing required fields).")
  }
}
```

## Write AMPL sensitivity AMPL command scripts

```{r write sensitivity AMPL scripts}
foreach(i = 1:nrow(params_totest_dat), .verbose = FALSE) %do% {
  
  tryCatch({
    param <- params_totest_dat[i, ]$param
    sets <- params_totest_dat[i, ]$sets
    member <- params_totest_dat[i, ]$member
    comidset <- params_totest_dat[i, ]$comidsets
    othersets <- params_totest_dat[i, ]$othersets
    
    # Debug print
    cat("Processing parameter:", param, "| sets:", sets, "| member:", member, "\n")
    
    ordersets <- params$param_sets[which(params$param_name == param)][[1]]
  sets_pos <- if(is.na(sets)) NA else str_locate(string = ordersets, pattern = sets)[1]
  comid_pos <- if(is.na(comidset)) NA else str_locate(string = ordersets, pattern = comidset)[1]
  
  # Fix: When othersets contains multiple sets, find position of the first one
  if(!is.na(othersets) && grepl(",", othersets)) {
    first_otherset <- strsplit(othersets, ",")[[1]][1]
    othersets_pos <- str_locate(string = ordersets, pattern = first_otherset)[1]
  } else {
    othersets_pos <- if(is.na(othersets)) NA else str_locate(string = ordersets, pattern = othersets)[1]
  }
  
  if(is.na(sets) && is.na(comidset) && is.na(othersets)) {
    sens_par <- param
  } else if(!is.na(sets) && is.na(comidset) && is.na(othersets)) {
    sens_par <- paste0(param, "['", member, "']")
  } else if(is.na(sets) && !is.na(comidset) && is.na(othersets)) {
    sens_par <- paste0(param, "[c]")
  } else if(!is.na(sets) && !is.na(comidset) && is.na(othersets)) {
    if(!is.na(sets_pos) && !is.na(comid_pos) && sets_pos < comid_pos) {
      sens_par <- paste0(param, "['", member, "', c]")
    } else if(!is.na(sets_pos) && !is.na(comid_pos) && sets_pos > comid_pos) {
      sens_par <- paste0(param, "[c, '", member, "']")
    } else {
      sens_par <- paste0(param, "['", member, "', c]")  # default case
    }
  } else if(!is.na(sets) && is.na(comidset) && !is.na(othersets)) {
    if(!is.na(sets_pos) && !is.na(othersets_pos) && sets_pos < othersets_pos) {
      sens_par <- paste0(param, "['", member, "', x]")
    } else if(!is.na(sets_pos) && !is.na(othersets_pos) && sets_pos > othersets_pos) {
      sens_par <- paste0(param, "[x, '", member, "']")
    } else {
      sens_par <- paste0(param, "['", member, "', x]")  # default case
    }
  } else if(!is.na(sets) && !is.na(comidset) && !is.na(othersets)) {
    if(!is.na(sets_pos) && !is.na(comid_pos) && !is.na(othersets_pos) && 
       sets_pos < comid_pos && sets_pos < othersets_pos && comid_pos < othersets_pos) {
      sens_par <- paste0(param, "['", member, "', c, x]")
    } else if(!is.na(sets_pos) && !is.na(comid_pos) && !is.na(othersets_pos) && 
              sets_pos < comid_pos && sets_pos < othersets_pos && comid_pos > othersets_pos) {
      sens_par <- paste0(param, "['", member, "', x, c]")
    } else if(!is.na(sets_pos) && !is.na(comid_pos) && !is.na(othersets_pos) && 
              sets_pos > comid_pos && sets_pos < othersets_pos && comid_pos < othersets_pos) {
      sens_par <- paste0(param, "[c, '", member, "', x]")
    } else if(!is.na(sets_pos) && !is.na(comid_pos) && !is.na(othersets_pos) && 
              sets_pos > comid_pos && sets_pos > othersets_pos && comid_pos < othersets_pos) {
      sens_par <- paste0(param, "[c, x, '", member, "']")
    } else if(!is.na(sets_pos) && !is.na(comid_pos) && !is.na(othersets_pos) && 
              sets_pos < comid_pos && sets_pos > othersets_pos && comid_pos > othersets_pos) {
      sens_par <- paste0(param, "[x, '", member, "', c]")
    } else if(!is.na(sets_pos) && !is.na(comid_pos) && !is.na(othersets_pos) && 
              sets_pos > comid_pos && sets_pos > othersets_pos && comid_pos > othersets_pos) {
      sens_par <- paste0(param, "[x, c, '", member, "']")
    } else {
      # Default case: member at the end (most common AMPL convention)
      sens_par <- paste0(param, "[c, x, '", member, "']")
    }
  } else {
    sens_par <- param  # fallback default
  }
  
  
  filename <- paste0("STcommand_sens-", substr(param, 1, 20), "-", substr(ifelse(is.na(member), "NA", member), 1, 25), ".amp")
  
  nchar(filename)
  
  # Parse othersets if it contains multiple comma-separated sets
  othersets_split <- if(!is.na(othersets)) {
    strsplit(othersets, ",")[[1]]
  } else {
    NA
  }
  
  # Generate loop variable names and index strings for multiple othersets
  if(!is.na(othersets) && length(othersets_split) > 1) {
    loop_vars <- c("x1", "x2", "x3", "x4")[1:length(othersets_split)]  # x1, x2, x3... for each set
    index_string <- paste(loop_vars, collapse = ", ")  # "x1, x2" for indexing
    
    # Build nested for loops opening
    nested_for_open <- paste(sapply(1:length(othersets_split), function(i) {
      paste0("for {", loop_vars[i], " in ", othersets_split[i], "} { ")
    }), collapse = "")
    
    # Build nested for loops closing
    nested_for_close <- paste(rep("}; ", length(othersets_split)), collapse = "")
    
    # Replace 'x' in sens_par with the expanded index string
    sens_par <- gsub("\\bx\\b", index_string, sens_par)
  } else {
    loop_vars <- "x"
    index_string <- "x"
    nested_for_open <- NULL
    nested_for_close <- NULL
  }
  
  cat(
    "
  #WMOST Optimization Screening Tool AMPL sensitivity analysis command file
set Sens;
let Sens := {0.01, 0.05, 0.06, 0.07, 0.08, 0.09, 0.1, 0.5, 0.6, 0.7, 0.8, 0.9, 0.95, 0.96, 0.97, 0.98, 0.99, 0.995, 0.996, 0.997, 0.998, 0.999, 1, 1.001, 1.002, 1.003, 1.004, 1.005, 1.01, 1.02, 1.03, 1.04, 1.05, 1.1, 1.2, 1.3, 1.4, 1.5, 2, 3, 4, 5, 10, 20, 30, 40, 50, 100};
",
if(is.na(comidset) && is.na(othersets)) {
  paste0("param SENSVALS {Sens};")
} else if(!is.na(comidset) && is.na(othersets)) {
  paste0("param SENSVALS {Sens, ", comidset, "};")
} else if(is.na(comidset) && !is.na(othersets)) {
  if(length(othersets_split) > 1) {
    paste0("param SENSVALS {Sens, ", paste(othersets_split, collapse = ", "), "};")
  } else {
    paste0("param SENSVALS {Sens, ", othersets, "};")
  }
} else if(!is.na(comidset) && !is.na(othersets)) {
  if(length(othersets_split) > 1) {
    paste0("param SENSVALS {Sens, ", comidset, ", ", paste(othersets_split, collapse = ", "), "};")
  } else {
    paste0("param SENSVALS {Sens, ", comidset, ", ", othersets, "};")
  }
}, 

"
param frac;
for {s in Sens} {
let frac := s;
",
if(is.na(comidset) && is.na(othersets)) {
  paste0("let SENSVALS[s] := frac * ", sens_par, ";")
} else if(!is.na(comidset) && is.na(othersets)) {
  paste0("for {c in ", comidset, "} { \n let SENSVALS[s, c] := frac * ", sens_par, "; \n };")
} else if(is.na(comidset) && !is.na(othersets)) {
  if(length(othersets_split) > 1) {
    paste0(nested_for_open, "\n let SENSVALS[s, ", index_string, "] := frac * ", sens_par, "; \n ", nested_for_close)
  } else {
    paste0("for {x in ", othersets, "} { \n let SENSVALS[s, x] := frac * ", sens_par, "; \n };")
  }
} else if(!is.na(comidset) && !is.na(othersets)) {
  if(length(othersets_split) > 1) {
    paste0(nested_for_open, "for {c in ", comidset, "} {\n let SENSVALS[s, c, ", index_string, "] := frac * ", sens_par, "; \n }; \n ", nested_for_close)
  } else {
    paste0("for {x in ", othersets, "} { for {c in ", comidset, "} {\n let SENSVALS[s, c, x] := frac * ", sens_par, "; \n }; \n };")
  }
}, 
"}
display SENSVALS;
for {s in Sens} {
let frac := s;
",
if(is.na(comidset) && is.na(othersets)) {
  paste0("let ", sens_par, " := SENSVALS[s];")
} else if(!is.na(comidset) && is.na(othersets)) {
  paste0("for {c in ", comidset, "} { \n let ", sens_par, " := SENSVALS[s, c]; \n };")
} else if(is.na(comidset) && !is.na(othersets)) {
  if(length(othersets_split) > 1) {
    paste0(nested_for_open, "\n let ", sens_par, " := SENSVALS[s, ", index_string, "]; \n ", nested_for_close)
  } else {
    paste0("for {x in ", othersets, "} { \n let ", sens_par, " := SENSVALS[s, x]; \n };")
  }
} else if(!is.na(comidset) && !is.na(othersets)) {
  if(length(othersets_split) > 1) {
    paste0(nested_for_open, "for {c in ", comidset, "} {\n let ", sens_par, " := SENSVALS[s, c, ", index_string, "]; \n }; \n ", nested_for_close)
  } else {
    paste0("for {x in ", othersets, "} { for {c in ", comidset, "} {\n let ", sens_par, " := SENSVALS[s, c, x]; \n }; \n };")
  }
},
"

solve;
option display_precision 10;
display frac;
display solve_result;
display cost;
",
if(is.na(comidset) && is.na(othersets)) {
  paste0("display ", sens_par, ";")
} else if(!is.na(comidset) && is.na(othersets)) {
  paste0("display {c in ", comidset, "} ", sens_par, ";")
} else if(is.na(comidset) && !is.na(othersets)) {
  if(length(othersets_split) > 1) {
    paste0("display {", paste(sapply(1:length(othersets_split), function(i) {
      paste0(loop_vars[i], " in ", othersets_split[i])
    }), collapse = ", "), "} ", sens_par, ";")
  } else {
    paste0("display {x in ", othersets, "} ", sens_par, ";")
  }
} else if(!is.na(comidset) && !is.na(othersets)) {
  if(length(othersets_split) > 1) {
    paste0("display {c in ", comidset, ", ", paste(sapply(1:length(othersets_split), function(i) {
      paste0(loop_vars[i], " in ", othersets_split[i])
    }), collapse = ", "), "} ", sens_par, ";")
  } else {
    paste0("display {c in ", comidset, ", x in ", othersets, "} ", sens_par, ";")
  }
},
"
option display_1col 10000000000;
option display_width 100000000000;
option omit_zero_rows 1;
option omit_zero_cols 1;
display seasons;
display years;
display sum {c in comid_all} (ps_coef[c] * point_dec[c]);
display {u in urban_bmp} sum {c in comid_all} (urban_coef[c,u] * urban_frac[c,u]);
display {a in ag_bmp} sum {c in comid_all} (ag_coef[c,a] * ag_frac[c,a]);
display {r in ripbuf_bmp} sum {c in comid_all} (ripbuf_coef[c, r] * ripbuf_length[c, r]);",
"}",
"
",
file = paste0(AMPLscriptsfolder, filename),
sep = "\n"
  )
  
  }, error = function(e) {
    cat("Error processing parameter", param, ":", e$message, "\n")
    return(NULL)
  })
  
}
```

## Send AMPL jobs to NEOS

```{r send AMPL scripts to solver}
# Function to submit individual sensitivity job with retry logic
submit_sensitivity_job <- function(i, cmdfiles, modc, datc, tmp, email, NEOSresults, max_retries = 3) {
  
  paramname <- str_extract(
    cmdfiles[i], pattern = "(?<=\\STcommand_sens-).+?(?=\\.amp)"
  )
  
  result_filepath <- paste0(NEOSresults, "NEOSresult_", paramname, ".txt")
  
  # Check if valid result already exists
  if (validate_result_file(result_filepath, c("cost =", "solve_result", "frac ="))) {
    cat("Result for", paramname, "already exists. Skipping.\n")
    return(TRUE)
  }
  
  comments <- paste(
    "sensitivity test of", 
    paramname, 
    " with all BMPs included and no user limits. Default loading targets."
  )
  
  for (attempt in 1:max_retries) {
    tryCatch({
      cat("Processing", paramname, "- Attempt", attempt, "of", max_retries, "\n")
      
      ## import command file contents
      comf <- cmdfiles[i]
      comc <- paste(paste(readLines(comf), collapse = "\n"), "\n")
      
      ## create list object
      argslist <- list(
        model = modc, data = datc, commands = comc, comments = comments, email = email
      )
      
      ## create XML string
      xmls <- CreateXmlString(neosxml = tmp, cdatalist = argslist)
      
      ## Submit job
      job.xml.text <- NsubmitJob(
        xmlstring = xmls, user = "rneos", interface = "", id = 0
      )
      
      ## Retrieve results
      resultfile <- NgetFinalResults(obj = job.xml.text, convert = TRUE)
      
      # Validate result content - only check if we got a response
      if (is.null(resultfile@ans) || length(resultfile@ans) == 0) {
        stop("Empty result returned from NEOS")
      }
      
      # Log the solve_result for informational purposes, but don't reject the result
      result_text <- paste(resultfile@ans, collapse = "\n")
      solve_result_match <- regmatches(result_text, regexpr("solve_result\\s*=\\s*\\w+", result_text))
      if (length(solve_result_match) > 0) {
        solve_result_value <- gsub(".*=\\s*", "", solve_result_match)
        if (grepl("infeasible", solve_result_value, ignore.case = TRUE)) {
          cat("Note:", paramname, "returned infeasible solution. Saving for troubleshooting.\n")
        }
      }
      
      # Write result file
      write.table(resultfile@ans, file = result_filepath)
      
      # Validate the written file has required structure
      if (validate_result_file(result_filepath, c("cost =", "solve_result", "frac ="))) {
        cat("Successfully saved result for", paramname, "on attempt", attempt, "\n")
        return(TRUE)
      } else {
        stop("Result file validation failed (missing required fields)")
      }
      
    }, error = function(e) {
      cat("Attempt", attempt, "failed for", paramname, ":", e$message, "\n")
      
      # Clean up potentially corrupted file (only if it's truly corrupted, not just infeasible)
      if (file.exists(result_filepath)) {
        if (!validate_result_file(result_filepath, c("cost =", "solve_result", "frac ="))) {
          file.remove(result_filepath)
          cat("Removed corrupted file for", paramname, "\n")
        }
      }
      
      if (attempt < max_retries) {
        delay <- 5 * (2 ^ (attempt - 1)) + runif(1, 0, 3)  # Exponential backoff with jitter
        cat("Waiting", round(delay, 1), "seconds before retry...\n")
        Sys.sleep(delay)
      } else {
        cat("All attempts failed for", paramname, "\n")
        return(FALSE)
      }
    })
  }
  return(FALSE)
}

# Function to check job completeness
check_job_completeness <- function(cmdfiles, NEOSresults) {
  
  completed_files <- list.files(
    path = NEOSresults, pattern = "NEOSresult_.*\\.txt", full.names = TRUE
  )
  completed_files <- completed_files[grep("_reference", completed_files, invert = TRUE)]
  
  check.completeness <- data.frame(cmdfile = cmdfiles) %>% 
    mutate(
      paramset = gsub(
        ".amp", 
        "", 
        gsub(
          paste0(AMPLscriptsfolder, "STcommand_sens-"),
          "", 
          cmdfile
        )
      ),
      expected_result = paste0(NEOSresults, "NEOSresult_", paramset, ".txt")
    ) %>%
    mutate(
      file_exists = file.exists(expected_result),
      file_valid = sapply(expected_result, function(f) {
        if (file.exists(f)) {
          validate_result_file(f, c("cost =", "solve_result", "frac ="))
        } else {
          FALSE
        }
      })
    )
  
  return(check.completeness)
}

cmdfiles <- list.files(
  path = AMPLscriptsfolder, pattern = "STcommand_sens", full.names = TRUE
) 

tmp <-my_NgetSolverTemplate(
  category = "lp", solvername = "CPLEX", inputMethod = "AMPL"
)
## setting path to model and data files
modf <- paste0(AMPLscriptsfolder,  "STmodel_seasonal.mod")
datf <- paste0(AMPLscriptsfolder, "STdata_seasonal.dat")

## enter email & comments
email <- "56407@icf.com"
## import file contents
modc <- paste(paste(readLines(modf), collapse = "\n"), "\n")
datc <- paste(paste(readLines(datf), collapse = "\n"), "\n")

# Main job submission loop with automatic retry
max_overall_retries <- 3
overall_attempt <- 1

while (overall_attempt <= max_overall_retries) {
  
  cat("\n=== Overall attempt", overall_attempt, "of", max_overall_retries, "===\n")
  
  # Check current completeness status
  completeness_check <- check_job_completeness(cmdfiles, NEOSresults)
  
  incomplete_jobs <- which(!completeness_check$file_valid)
  
  if (length(incomplete_jobs) == 0) {
    cat("All jobs completed successfully!\n")
    break
  }
  
  cat("Found", length(incomplete_jobs), "incomplete jobs out of", length(cmdfiles), "total jobs.\n")
  
  # Process incomplete jobs
  failed_jobs <- c()
  
  # Use parallel processing for efficiency, but limit concurrent jobs to avoid overwhelming NEOS
  if (length(incomplete_jobs) > 10) {
    # For large numbers of jobs, process in smaller batches
    batch_size <- 5
    batches <- split(incomplete_jobs, ceiling(seq_along(incomplete_jobs) / batch_size))
    
    for (batch in batches) {
      cat("Processing batch of", length(batch), "jobs...\n")
      
      batch_results <- foreach(i = batch, .packages = c("tidyverse", "rneos"), .combine = "c") %dopar% {
        options(RCurlOptions = list(ssl.verifypeer = FALSE))
        submit_sensitivity_job(i, cmdfiles, modc, datc, tmp, email, NEOSresults)
      }
      
      failed_in_batch <- batch[!batch_results]
      failed_jobs <- c(failed_jobs, failed_in_batch)
      
      # Brief pause between batches
      if (length(batches) > 1) {
        Sys.sleep(10)
      }
    }
    
  } else {
    # For smaller numbers, process in parallel
    job_results <- foreach(i = incomplete_jobs, .packages = c("tidyverse", "rneos"), .combine = "c") %dopar% {
      options(RCurlOptions = list(ssl.verifypeer = FALSE))
      submit_sensitivity_job(i, cmdfiles, modc, datc, tmp, email, NEOSresults)
    }
    
    failed_jobs <- incomplete_jobs[!job_results]
  }
  
  if (length(failed_jobs) == 0) {
    cat("All remaining jobs completed successfully!\n")
    break
  } else {
    cat("Still have", length(failed_jobs), "failed jobs after attempt", overall_attempt, "\n")
    
    if (overall_attempt < max_overall_retries) {
      wait_time <- 30 * overall_attempt
      cat("Waiting", wait_time, "seconds before next overall retry...\n")
      Sys.sleep(wait_time)
    }
  }
  
  overall_attempt <- overall_attempt + 1
}

# Final completeness check and summary
final_check <- check_job_completeness(cmdfiles, NEOSresults)
successful_jobs <- sum(final_check$file_valid)
total_jobs <- nrow(final_check)

cat("\n=== FINAL SUMMARY ===\n")
cat("Successfully completed:", successful_jobs, "out of", total_jobs, "jobs\n")

# Count infeasible solutions separately
infeasible_jobs <- 0
for (i in which(final_check$file_valid)) {
  filepath <- final_check$expected_result[i]
  if (file.exists(filepath)) {
    content <- paste(readLines(filepath, warn = FALSE), collapse = "\n")
    if (grepl("solve_result\\s*=\\s*infeasible", content, ignore.case = TRUE)) {
      infeasible_jobs <- infeasible_jobs + 1
    }
  }
}

if (infeasible_jobs > 0) {
  cat("Note:", infeasible_jobs, "jobs returned infeasible solutions (saved for troubleshooting).\n")
}

if (successful_jobs < total_jobs) {
  failed_job_details <- final_check[!final_check$file_valid, ]
  cat("Failed jobs (missing required fields):\n")
  for (i in 1:nrow(failed_job_details)) {
    cat(" -", failed_job_details$paramset[i], "\n")
  }
  
  # Save failed job list for manual review
  write.csv(failed_job_details, file = paste0(NEOSresults, "failed_jobs_log.csv"), row.names = FALSE)
  cat("Failed job details saved to:", paste0(NEOSresults, "failed_jobs_log.csv"), "\n")
} else {
  cat("All jobs completed and saved successfully!\n")
}
```

## Load Reference Data and AMPL model
```{r load reference file}
dat <- fread(
  file = paste0(NEOSresults, "NEOSresult_reference.txt"),
  fill = TRUE,
  sep = "\t",
  sep2 = "\n",
  quote = ""
) %>% 
  rename(X = 1)
dat <- as.data.frame(dat)

```

## Parse Reference File
Creates data frames for the reference result ag, urban, riparian buffer, and septic bmps.
```{r parse reference file}

full.list.of.BMPs <- c(
  unique(
    (
      params_totest_dat %>% 
        filter(sets %in% c("urban_bmp", "ripbuf_bmp", "ag_bmp", "septic_bmp"))
    )$member
  ),  
  "WWTP_upgrades"
)

ref.cost <- as.numeric(
  gsub("cost = ", "", dat$X[which(grepl("cost =", dat$X))])
)

end.rows <- which(grepl(";", dat$X))
BMPdescriptions_begin <- which(grepl("sum[{]c in comid_all[}]", dat$X)) 
which_point <- grep("point", dat$X[BMPdescriptions_begin])
which_ag <- grep("ag", dat$X[BMPdescriptions_begin])
which_urban <- grep("urban", dat$X[BMPdescriptions_begin])
which_ripbuf <- grep("ripbuf", dat$X[BMPdescriptions_begin])
which_septic <- grep("septic", dat$X[BMPdescriptions_begin])
BMP <- c()
BMP[which_point] <- "point"
BMP[which_ag] <- "ag"
BMP[which_urban] <- "urban"
BMP[which_ripbuf] <- "ripbuf"
BMP[which_septic] <- "septic"

BMP.end.rows <- which(grepl(";", dat$X))

frac.summary <- data.frame(
  frac = 1,
  solve_result = 1,
  cost = ref.cost
) %>%
  mutate(
    cost = case_when(solve_result == 0 ~ NA_real_, solve_result == 1 ~ cost)
  )

BMPdescriptions_end <- foreach(
  i = 1:length(BMPdescriptions_begin), .combine = "c"
) %do% {
  if(i %in% which_point) {tmp <- BMPdescriptions_begin[i]} else {
    tmp <- BMP.end.rows[min(which(BMP.end.rows > BMPdescriptions_begin[i]))]
  }
  tmp
}

BMPspending_summary <- foreach(i = 1:length(BMPdescriptions_begin), .combine = "rbind") %do% {
  tmp <- dat[BMPdescriptions_begin[i]:BMPdescriptions_end[i],1]
  if(i %in% which_point) {
    bee <- as.numeric(str_split_fixed(tmp, " = ", n = 2)[2])
    tmp.dat <- data_frame(frac = ceiling(i / 4), BMP = "WWTP_upgrades", Total_Spent = bee)
  } else if(length(tmp) > 2) {
    tmp.clean <- str_split_fixed(parse_character(tmp[2:(length(tmp)-1)]), " ", n = 2)
    BMP <- parse_character(tmp.clean[,1])
    costs <- parse_number(tmp.clean[,2])
    
    tmp.dat <- data_frame(frac = ceiling(i / 4), BMP = BMP, Total_Spent = costs)
  } else {tmp.dat <- NULL}
  tmp.dat
}

BMPspending_summary_reference <- BMPspending_summary %>%
  full_join(., BMPspending_summary %>% expand(frac, BMP = full.list.of.BMPs)) %>%
  mutate(
    Total_Spent = case_when(
      is.na(Total_Spent) ~ 0, !is.na(Total_Spent) ~ Total_Spent
    ),
    BMP_Category = case_when(
      BMP %in% c("WWTP_upgrades") ~ "Point Source BMPs",
      BMP %in% c("Grassed_Buffer", "Forested_Buffer") ~ "Riparian Buffer BMPs",
      BMP %in% c("Biofiltration_w_Underdrain", "Bioretention_Basin", "Enhanced_Biofiltration_w_ISR", "Extended_Dry_Detention_Basin", "Grass_Swale_w_detention", "Gravel_Wetland", "Infiltration_Basin", "Infiltration_Chamber", "Infiltration_Trench", "Porous_Pavement_w_subsurface_infiltration", "Porous_Pavement_w_underdrain", "Sand_Filter_w_underdrain", "Wet_Pond") ~ "Urban BMPs",
      BMP %in% c("Conservation", "Contour_Farming", "Fert_20", "Filterstrip", "Manure_Injection", "MIN_TILL", "Ponds", "Terrace_Only", "Terrace_Waterway", "Waterway_Only") ~ "Agricultural BMPs",
      BMP %in% c("class_1_upgrade", "class_2_upgrade", "class_3_upgrade", "class_4_upgrade", "class_5_upgrade", "class_6_upgrade", "class_7_upgrade", "class_8_upgrade", "Sewer_convert") ~ "Septic BMPs"
    )
  ) %>%
  left_join(., frac.summary, by = "frac") %>%
  filter(solve_result == 1)

``` 

## Load & Parse NEOS results

```{r load & parse sens files}
# Function to safely parse a single result file
parse_single_result_file <- function(file_path, max_retries = 2) {
  
  for (attempt in 1:max_retries) {
    tryCatch({
      
      param <- gsub(
        x = gsub(
          x = file_path,
          pattern = paste0(NEOSresults, "NEOSresult_"),
          replacement = ""
        ),
        pattern = ".txt",
        replacement = ""
      )
      
      # Validate file before processing
      if (!validate_result_file(file_path, c("cost =", "solve_result", "frac ="))) {
        stop("File validation failed")
      }
      
      dat <- fread(file_path, fill = TRUE, skip = 2, sep = "\t", sep2 = "\n") %>%
        rename(X = 1)
      
      if(ncol(dat) > 1) {
        dat$X <- apply(X = dat[,1:ncol(dat)], MARGIN = 1, FUN = paste, collapse = " ")
        dat <- dat %>% select(X)
      }
      
      dat.split <- dat %>%
        mutate(
          new.group = case_when(
            (
              grepl(x = X, pattern = "frac = ") &
                !grepl(x = X, pattern = "_frac") &
                !grepl(x = X, pattern = "frac_")
            ) ~ TRUE,
            TRUE ~ FALSE
          ),
          group = cumsum(new.group)
        ) %>%
        filter(group > 0) %>%
        group_split(group)
      
      if (length(dat.split) == 0) {
        stop("No valid data groups found in file")
      }
      
      dat.split.parsed <- data.frame()
      
      for(j in 1:length(dat.split)) {
        tryCatch({
          dat.tmp <- as.data.frame(dat.split[[j]])
          
          frac <- as.numeric(
            str_extract(
              string = dat.tmp[
                which(
                  sapply(dat.tmp, grepl, pattern = "frac =") &
                    !sapply(dat.tmp, grepl, pattern = "agcost_frac =")
                ),
                1
              ],
              pattern = "(?i)(?<=frac =\\D)[[:digit:]]+\\.*[[:digit:]]*"
            )
          )
          
          if (is.na(frac)) {
            warning(paste("Could not extract frac value for group", j, "in file", file_path))
            next
          }
          
          solve.result = gsub(
            " ",
            "",
            gsub(
              "solve_result = ",
              "",
              dat.tmp$X[which(grepl("solve_result =", dat.tmp$X))]
            )
          )
          
          ref.cost <- as.numeric(
            gsub(
              "cost = ",
              "",
              dat.tmp$X[which(grepl("cost =", dat.tmp$X))]
            )
          )
          
          # Skip if critical values are missing
          if (length(solve.result) == 0 || is.na(ref.cost)) {
            warning(paste("Missing critical values for group", j, "in file", file_path))
            next
          }
          
          end.rows <- which(sapply(dat.tmp, grepl, pattern = ";"))
          
          BMPdescriptions_begin <- which(
            sapply(dat.tmp, grepl, pattern = "sum[{]c in comid_all[}]")
          )
          which_point <- grep("point", dat.tmp[BMPdescriptions_begin,1])
          which_ag <- grep("ag", dat.tmp[BMPdescriptions_begin,1])
          which_urban <- grep("urban", dat.tmp[BMPdescriptions_begin,1])
          which_ripbuf <- grep("ripbuf", dat.tmp[BMPdescriptions_begin,1])
          which_septic <- grep("septic", dat.tmp[BMPdescriptions_begin,1])
          BMP <- c()
          BMP[which_point] <- "point"
          BMP[which_ag] <- "ag"
          BMP[which_urban] <- "urban"
          BMP[which_ripbuf] <- "ripbuf"
          BMP[which_septic] <- "septic"
          
          BMP.end.rows <- which(sapply(dat.tmp$X, grepl, pattern = ";"))
          
          frac.summary <- data.frame(
            frac = frac,
            solve_result = solve.result,
            cost = ref.cost
          ) %>%
            mutate(
              cost = case_when(
                solve_result == "infeasible" ~ NA_real_,
                solve_result == "solved" ~ cost
              )
            )
          
          BMPdescriptions_end <- numeric(length(BMPdescriptions_begin))
          for(k in 1:length(BMPdescriptions_begin)) {
            if(k %in% which_point) {
              BMPdescriptions_end[k] <- BMPdescriptions_begin[k]
            } else {
              BMPdescriptions_end[k] <- BMP.end.rows[min(which(BMP.end.rows > BMPdescriptions_begin[k]))]
            }
          }
          
          BMPspending_summary <- data.frame()
          for(k in 1:length(BMPdescriptions_begin)) {
            tmp <- dat.tmp[BMPdescriptions_begin[k]:BMPdescriptions_end[k],1]
            
            if(k %in% which_point) {
              bee <- as.numeric(str_split_fixed(tmp, " = ", n = 2)[2])
              if (!is.na(bee)) {
                tmp.dat <- data_frame(
                  frac = frac, BMP = "WWTP_upgrades", Total_Spent = bee
                )
              } else {
                tmp.dat <- NULL
              }
            } else if(length(tmp) > 2) {
              tmp.clean <- str_split_fixed(
                parse_character(tmp[2:(length(tmp)-1)]), " ", n = 2
              )
              BMP <- parse_character(tmp.clean[,1])
              costs <- parse_number(tmp.clean[,2])
              
              # Filter out any NA values
              valid_indices <- !is.na(BMP) & !is.na(costs)
              if (any(valid_indices)) {
                tmp.dat <- data_frame(
                  frac = frac, 
                  BMP = BMP[valid_indices], 
                  Total_Spent = costs[valid_indices]
                )
              } else {
                tmp.dat <- NULL
              }
            } else {
              tmp.dat <- NULL
            }
            
            if(!is.null(tmp.dat)) {
              BMPspending_summary <- rbind(BMPspending_summary, tmp.dat)
            }
          }
          
          if (nrow(BMPspending_summary) > 0) {
            BMPspending_summary_full <- BMPspending_summary %>%
              full_join(
                ., BMPspending_summary %>% expand(frac, BMP = full.list.of.BMPs), by = c("frac", "BMP")
              ) %>%
              mutate(
                Total_Spent = case_when(
                  is.na(Total_Spent) ~ 0, !is.na(Total_Spent) ~ Total_Spent
                ),
                BMP_Category = case_when(
                  BMP %in% c("WWTP_upgrades") ~ "Point Source BMPs",
                  BMP %in% c("Grassed_Buffer", "Forested_Buffer") ~
                    "Riparian Buffer BMPs",
                  BMP %in% c(
                    "Biofiltration_w_Underdrain",
                    "Bioretention_Basin",
                    "Enhanced_Biofiltration_w_ISR",
                    "Extended_Dry_Detention_Basin",
                    "Grass_Swale_w_detention",
                    "Gravel_Wetland",
                    "Infiltration_Basin",
                    "Infiltration_Chamber",
                    "Infiltration_Trench",
                    "Porous_Pavement_w_subsurface_infiltration",
                    "Porous_Pavement_w_underdrain",
                    "Sand_Filter_w_underdrain",
                    "Wet_Pond"
                  ) ~ "Urban BMPs",
                  BMP %in% c(
                    "Conservation",
                    "Contour_Farming",
                    "Fert_20",
                    "Filterstrip",
                    "Manure_Injection",
                    "MIN_TILL", "Ponds",
                    "Terrace_Only",
                    "Terrace_Waterway",
                    "Waterway_Only"
                  ) ~ "Agricultural BMPs",
                  BMP %in% c(
                    "class_1_upgrade",
                    "class_2_upgrade",
                    "class_3_upgrade",
                    "class_4_upgrade",
                    "class_5_upgrade",
                    "class_6_upgrade",
                    "class_7_upgrade",
                    "class_8_upgrade",
                    "Sewer_convert"
                  ) ~ "Septic BMPs"
                ),
                param = param
              ) %>%
              left_join(., frac.summary, by = "frac") %>%
              filter(solve_result == "solved") %>%
              mutate(
                setmember = unlist(lapply(str_split(param, pattern = "-"), "[[", 2)),
                param = unlist(lapply(str_split(param, pattern = "-"), "[[", 1))
              )
            
            dat.split.parsed <- rbind(dat.split.parsed, BMPspending_summary_full)
          }
          
        }, error = function(e) {
          warning(paste("Error processing inner loop j =", j, "for file", file_path, ":", e$message))
        })
      }
      
      cat("Successfully parsed:", param, "(", nrow(dat.split.parsed), "rows )\n")
      return(dat.split.parsed)
      
    }, error = function(e) {
      warning(paste("Attempt", attempt, "failed for file", file_path, ":", e$message))
      
      if (attempt < max_retries) {
        Sys.sleep(1)  # Brief pause before retry
      } else {
        cat("Failed to parse file:", file_path, "\n")
        return(data.frame())  # Return empty data frame for failed files
      }
    })
  }
  
  return(data.frame())  # Return empty if all attempts failed
}

# Get list of result files
list.results <- list.files(
  path = NEOSresults, pattern = "NEOSresult_*", full.names = TRUE
)

list.results <- list.results[grep("_reference", list.results, invert = TRUE)]

# Filter out any files that don't pass validation
valid_files <- sapply(list.results, function(f) {
  validate_result_file(f, c("cost =", "solve_result", "frac ="))
})

list.results <- list.results[valid_files]

cat("Found", length(list.results), "valid result files to process.\n")

if (length(list.results) == 0) {
  stop("No valid result files found. Please check NEOS job submissions.")
}

# Process files with progress tracking
all.results <- data.frame()
error_files <- character()
successful_files <- 0

for(i in 1:length(list.results)) {
  cat("Processing file", i, "of", length(list.results), "...\n")
  
  result_data <- parse_single_result_file(list.results[i])
  
  if (nrow(result_data) > 0) {
    all.results <- rbind(all.results, result_data)
    successful_files <- successful_files + 1
  } else {
    error_files <- c(error_files, list.results[i])
  }
}

# Summary
cat("\n=== PARSING SUMMARY ===\n")
cat("Successfully parsed:", successful_files, "out of", length(list.results), "files\n")
cat("Total rows in final dataset:", nrow(all.results), "\n")

if(length(error_files) > 0) {
  cat("\nFiles with parsing errors:\n")
  for(file in error_files) {
    cat(" -", basename(file), "\n")
  }
  
  # Save error log
  error_log <- data.frame(
    error_file = error_files,
    timestamp = Sys.time()
  )
  write.csv(error_log, file = paste0(NEOSresults, "parsing_errors_log.csv"), row.names = FALSE)
  cat("Error log saved to:", paste0(NEOSresults, "parsing_errors_log.csv"), "\n")
} else {
  cat("All files processed successfully!\n")
}

# Validate final results
if (nrow(all.results) == 0) {
  stop("No data was successfully parsed. Please check result files and parsing logic.")
}

# Check for reasonable data ranges
param_counts <- all.results %>% 
  group_by(param, setmember) %>% 
  summarize(n_observations = n(), .groups = "drop")

cat("\nParameter observation counts:\n")
print(param_counts)

# Save results
save(all.results, file = paste0(NEOSresults, "all_results.RDa"))
cat("\nResults saved to:", paste0(NEOSresults, "all_results.RDa"), "\n")

# For subsequent analysis, load the saved results
all.results <- get(load(paste0(NEOSresults, "all_results.RDa")))
```

## Parse NEOS sensitivity results
```{r}
all.results.compare <- all.results %>%
  left_join(
    ., 
    BMPspending_summary_reference %>% 
      select(BMP, Total_Spent, BMP_Category, cost),
    by = c("BMP", "BMP_Category"), suffix = c("_sens", "_ref")
  ) 

all.costs <- all.results.compare %>%
  group_by(param, setmember, frac) %>%
  summarize(cost_sens = mean(cost_sens), cost_ref = mean(cost_ref))  %>%
  mutate(
    param = case_when(
      param == "ripbuf_costs_operati" ~ "ripbuf_costs_operations",
      param == "unbuffered_banklengt" ~ "unbuffered_banklength",
      param == "urban_bmp_implementa" ~ "urban_bmp_implementationpotential",
      param == "urban_cost_adjustmen" ~ "urban_cost_adjustment_coef",
      TRUE ~ param
    ),
    setmember = case_when(
      setmember == "Biofiltration_w_Underdrai" ~ "Biofiltration_w_Underdrain",
      setmember == "Enhanced_Biofiltration_w_" ~ "Enhanced_Biofiltration_w_ISR",
      setmember == "Extended_Dry_Detention_Ba" ~ "Extended_Dry_Detention_Basin",
      setmember == "Porous_Pavement_w_subsurf" ~ 
        "Porous_Pavement_w_subsurface_infiltration",
      setmember == "Porous_Pavement_w_underdr" ~ "Porous_Pavement_w_underdrain",
      TRUE ~ setmember
    ),
    param_source = case_when(
      param %in% c(
        "ag_frac_max", 
        "ag_frac_min", 
        "loads_lim_N1", 
        "loads_lim_P1", 
        "loads_lim_P2",
        "ripbuf_frac_max",
        "ripbuf_frac_min",
        "urban_design_depth", 
        "urban_frac_max",
        "urban_frac_min"
      ) ~ 
        "User Supplied", 
      TRUE ~ "Provided Data"
    )
  )

tolerance.ranges_cost <- all.costs %>%
  mutate(
    percent_difference = (cost_ref - cost_sens) / cost_ref
  ) %>%
  filter(abs(percent_difference) <= 0.1) %>%
  group_by(param, setmember) %>%
  summarize(tolerance_low = min(frac), tolerance_high = max(frac)) 

all.spatial <- all.results.compare %>%
  mutate(
    percent_difference = case_when(
      Total_Spent_ref != 0 ~ 
        (Total_Spent_ref - Total_Spent_sens) / Total_Spent_ref, 
      Total_Spent_ref == 0 ~ 
        case_when(Total_Spent_sens == 0  ~ 0, Total_Spent_sens != 0 ~ Inf)
    )
  ) %>%
  mutate(
    param = case_when(
      param == "ripbuf_costs_operati" ~ "ripbuf_costs_operations",
      param == "unbuffered_banklengt" ~ "unbuffered_banklength",
      param == "urban_bmp_implementa" ~ "urban_bmp_implementationpotential",
      param == "urban_cost_adjustmen" ~ "urban_cost_adjustment_coef",
      TRUE ~ param
    ),
    setmember = case_when(
      setmember == "Biofiltration_w_Underdrai" ~ "Biofiltration_w_Underdrain",
      setmember == "Enhanced_Biofiltration_w_" ~ "Enhanced_Biofiltration_w_ISR",
      setmember == "Extended_Dry_Detention_Ba" ~ "Extended_Dry_Detention_Basin",
      setmember == "Porous_Pavement_w_subsurf" ~ 
        "Porous_Pavement_w_subsurface_infiltration",
      setmember == "Porous_Pavement_w_underdr" ~ "Porous_Pavement_w_underdrain",
      TRUE ~ setmember
    ),
    param_source = case_when(
      param %in% c(
        "ag_frac_max", 
        "ag_frac_min", 
        "loads_lim_N1", 
        "loads_lim_P1", "
        loads_lim_P2",
        "ripbuf_frac_max",
        "ripbuf_frac_min",
        "urban_design_depth", 
        "urban_frac_max",
        "urban_frac_min"
      ) ~ 
        "User Supplied", 
      TRUE ~ "Provided Data"
    )
  )


tolerance.ranges_spatial <- all.spatial %>%
  filter(abs(percent_difference) <= 0.1 ) %>%
  group_by(param, setmember, BMP) %>%
  summarize(
    tolerance_low_byBMP = min(frac), tolerance_high_byBMP = max(frac)
  ) %>%
  ungroup() %>%
  group_by(param, setmember) %>%
  summarize(
    tolerance_low = max(tolerance_low_byBMP), 
    tolerance_high = min(tolerance_high_byBMP)
  )

tolerance.ranges <- full_join(
  tolerance.ranges_cost, 
  tolerance.ranges_spatial, 
  by = c("param", "setmember"), 
  suffix = c(".cost", ".spatial")
) %>%
  rowwise() %>%
  mutate(
    tolerance_low = max(tolerance_low.cost, tolerance_low.spatial),
    tolerance_high = min(tolerance_high.cost, tolerance_high.spatial),
    param_source = case_when(
      param %in% c(
        "ag_frac_max", 
        "ag_frac_min", 
        "loads_lim_N1", 
        "loads_lim_P1", 
        "loads_lim_P2",
        "ripbuf_frac_max",
        "ripbuf_frac_min",
        "urban_design_depth", 
        "urban_frac_max",
        "urban_frac_min"
      ) ~ 
        "User Supplied", 
      TRUE ~ "Provided Data"
    ),
    lowendtolerance = case_when(
      param %in% c(
        "ag_frac_min", 
        "point_effic_P", 
        "ripbuf_costs_operati",
        "ripbuf_frac_min", 
        "urban_frac_min"
      ) ~ "not applicable",
      tolerance_low >= 0.99 ~ "highly sensitive",
      tolerance_low >= 0.9 ~ "sensitive",
      tolerance_low < 0.9 ~ "not sensitive"
    ),
    highendtolerance = case_when(
      param %in% c(
        "ag_frac_min", 
        "point_effic_P", 
        "ripbuf_costs_operati",
        "ripbuf_frac_min", 
        "urban_frac_min",
        "ag_frac_max",
        "urban_frac_max",
        "ripbuf_frac_max"
      ) ~ "not applicable",
      tolerance_high <= 1.01 ~ "highly sensitive",
      tolerance_high <= 1.1 ~ "sensitive",
      tolerance_high > 1.1 ~ "not sensitive"
    )
  ) %>%
  mutate(
    param = case_when(
      param == "ripbuf_costs_operati" ~ "ripbuf_costs_operations",
      param == "unbuffered_banklengt" ~ "unbuffered_banklength",
      param == "urban_bmp_implementa" ~ "urban_bmp_implementationpotential",
      param == "urban_cost_adjustmen" ~ "urban_cost_adjustment_coef",
      TRUE ~ param
    ),
    setmember = case_when(
      setmember == "Biofiltration_w_Underdrai" ~ "Biofiltration_w_Underdrain",
      setmember == "Enhanced_Biofiltration_w_" ~ "Enhanced_Biofiltration_w_ISR",
      setmember == "Extended_Dry_Detention_Ba" ~ "Extended_Dry_Detention_Basin",
      setmember == "Porous_Pavement_w_subsurf" ~ 
        "Porous_Pavement_w_subsurface_infiltration",
      setmember == "Porous_Pavement_w_underdr" ~ "Porous_Pavement_w_underdrain",
      TRUE ~ setmember
    )
  )

```
## Summarize Tolerance Ranges
```{r}
tolerance.ranges %>% 
  mutate(range = log10(tolerance_high) - log10(tolerance_low)) %>%
  arrange(range)
tolerance.ranges %>% 
  mutate(range = log10(tolerance_high) - log10(tolerance_low)) %>%
  group_by(param) %>%
  summarize(median_range = median(range)) %>%
  arrange(median_range)
tolerance.ranges %>% 
  mutate(range = log10(tolerance_high) - log10(tolerance_low)) %>%
  group_by(setmember) %>%
  summarize(median_range = median(range)) %>%
  arrange(median_range)

tolerance.ranges %>%
  group_by(param) %>%
  mutate(mean_low = mean(tolerance_low), mean_high = mean(tolerance_high)) %>%
  filter(mean_low > 0.9, mean_high <1.1)

tolerance.ranges %>%
  group_by(param) %>%
  summarize(mean_low = mean(tolerance_low), mean_high = mean(tolerance_high)) %>%
  filter(mean_low > 0.9, mean_high <1.1)

tolerance.ranges %>%
  group_by(param) %>%
  summarize(mean_low = mean(tolerance_low), mean_high = mean(tolerance_high)) %>%
  filter(mean_low > 0.99, mean_high <1.01)

tolerance.ranges %>%
  filter(tolerance_low >= 0.99, tolerance_high <= 1.01)
```


## Plot tolerance ranges by parameter value
```{r sensfigs}
setmember_shapes <- c(1:25, 1, 2, 3, 4, 7, 11)

# Get tolerance range based on cost
lowendtolrange <- mean(all.costs$cost_ref) * 0.9
highendtolrange <- mean(all.costs$cost_ref) * 1.1

## View Sensitivity of Cost to all Parameters
cost.sens <- ggplot(
  # data = all.costs, 
  data = all.costs %>% 
    filter(
      # param_source == "Provided Data",
      param %in% c(
        "agcost_frac",   # This selection of parameters are those with tolerance ranges <10%
        "area",
        "baseloads_N1",
        "loads_lim_N1",
        "other_loads_N1",
        "riparianremoval_N1",
        "ripbuf_costs_capital",
        "ripbuf_frac_max",
        "runoff_coeff_urban",
        "unbuffered_banklength",
        "urban_cost_adjustment_coef"
      )
    ) %>%
    ungroup() %>%
    group_by(param, frac) %>%
    summarize(cost_sens = mean(cost_sens)) %>%
    mutate(
      param = case_when(
        param %in% c("runoff_coeff_urban", "urban_cost_adjustment_coef") ~
          "runoff_coeff_urban and urban_cost_adjustment_coef",
        param %in% c(
          "unbuffered_banklength", "ripbuf_costs_capital", "ripbuf_frac_max"
        ) ~
          "ripbuf_costs_capital, ripbuf_frac_max, and unbuffered_banklength",
        TRUE ~ param
      )
    ),
  mapping = aes(
    x = frac, y = cost_sens, color = param
  )
) + 
  annotate(
    "rect",
    xmin = 0.01, xmax = 100, ymin = lowendtolrange, ymax = highendtolrange,
    fill = "grey95"
  ) +
  geom_line(show.legend = TRUE, lwd = 1) +
  # geom_point(size = 3, show.legend = FALSE) +
  # geom_smooth(se = FALSE, method = "loess", lwd = 2, formula = "y~x") +
  scale_x_log10(
    name = "Fraction of Original", 
    breaks = c(0.01, 0.1, 1, 10, 100), 
    labels = c("0.01", "0.1", "1", "10", "100")
  ) +
  scale_color_brewer(palette = "Set1") +
  # facet_wrap(facets = c("param", "setmember"), ncol = 4) + #scales = "free_y"
  # facet_wrap(facets = c("param"), ncol = 4) + #scales = "free_y"
  scale_y_log10(
    name = "Total Annualized Cost (x $1,000,000)",
    breaks = c(100000, 1000000, 10000000, 100000000, 1000000000), 
    labels = c("$0.1", "$1", "$10", "$100", "$1,000")
  ) +
  theme(legend.position = "bottom", legend.direction = "vertical") 

print(cost.sens)

# 
# 
## View Sensitivity of Spatial to all Parameters
space.sens <- ggplot(
  data = all.spatial %>% 
    filter(
      # param_source == "Provided Data",
      param %in% c(
        "agcost_frac",   # This selection of parameters are those with tolerance ranges <10%
        "area",
        "baseloads_N1",
        "loads_lim_N1",
        "other_loads_N1",
        "riparianremoval_N1",
        "ripbuf_costs_capital",
        "ripbuf_frac_max",
        "runoff_coeff_urban",
        "unbuffered_banklength",
        "urban_cost_adjustment_coef"
      )
    ) %>%
    ungroup() %>%
    group_by(param, frac) %>%
    # mutate(
    #   percent_difference = case_when(
    #     !is.infinite(percent_difference) ~ percent_difference,
    #     is.infinite(percent_difference) ~ 1000000
    #   )
    #     ) %>%
    summarize(spatial_sens = max(abs(percent_difference))) %>%
    mutate(
      param = case_when(
        param %in% c("runoff_coeff_urban", "urban_cost_adjustment_coef") ~
          "runoff_coeff_urban and urban_cost_adjustment_coef",
        param %in% c(
          "unbuffered_banklength", "ripbuf_costs_capital", "ripbuf_frac_max"
        ) ~
          "ripbuf_costs_capital, ripbuf_frac_max, and unbuffered_banklength",
        TRUE ~ param
      )
    ) %>%
    drop_na(),
  mapping = aes(
    x = frac,
    y = abs(spatial_sens),
    color = param
  )
) +
  geom_rect(
    inherit.aes = FALSE,
    mapping = aes(
      xmin = 0.01, xmax = 100, ymin = 0, ymax = 0.1
    ),
    fill = "grey95"
  ) +
  geom_line(show.legend = FALSE, lwd = 1) +
  # geom_point(size = 3, show.legend = FALSE) +
  # geom_smooth(se = FALSE, method = "loess", lwd = 2, formula = "y~x") +
  scale_x_continuous(
    trans = "log10",
    name = "Fraction of Original", 
    breaks = c(0.01, 0.1, 1, 10, 100), 
    labels = c("0.01", "0.1", "1", "10", "100")
  ) +
  scale_color_brewer(palette = "Set1") +
  # facet_wrap(facets = c("param", "setmember"), ncol = 4) + #scales = "free_y"
  # facet_wrap(facets = c("param"), ncol = 4) + #scales = "free_y"
  scale_y_continuous(
    trans = "log10", 
    name = "Optimized spending per BMP / default", 
    limits = c(0.001, 1)
  ) 

print(space.sens)

# 
# ## View Tolerance Range as fractions
# tolerance_ranges <- ggplot(
#   data = tolerance.ranges, 
#   mapping = aes(x = tolerance_low, y = tolerance_high, color = param, shape = setmember)
# ) + 
#   geom_point(size = 5, show.legend = TRUE, alpha = 0.5) +
#   scale_shape_manual(values = setmember_shapes) +
#   labs(
#     title = "Local Sensitivity Parameter Tolerance", 
#     color = "Parameter"
#   ) +
#   scale_x_log10(
#     name = "Tolerance Range Low End (as fraction of default value)", 
#     lim = c(0.01,1)
#   ) + 
#   scale_y_log10(
#     name = "Tolerance Range High End (as fraction of default value)", 
#     lim = c(1, 100)
#   ) +
#   geom_hline(yintercept = 1.1, color = "grey", lty = 2) + 
#   geom_vline(xintercept = 0.9, color = "grey", lty = 2) +
#   annotate("text", x = 1, y = 1, label = "Highly Sensitive") +
#   annotate("text", x = 0.1, y = 1, label = "Sensitive to Higher Values") +
#   annotate("text", x = 1, y = 10, label = "Sensitive to Lower Values") +
#   annotate("text", x = 0.1, y = 10, label = "Not Sensitive") +
#   facet_wrap("param_source")
# ggsave(
#   plot = tolerance_ranges, 
#   filename = paste0(figureoutputs, "ToleranceRanges.png"), 
#   width = 16,
#   height = 10,
#   units = "in",
#   limitsize = FALSE
# )
# 
# nb.cols <- 16
# mycolors <- colorRampPalette(brewer.pal(8, "Set3"))(nb.cols)
# 
# tolerance.zoom <- ggplot(
#   data = tolerance.ranges %>% filter(tolerance_low > 0.9 & tolerance_high < 1.1), 
#   mapping = aes(x = tolerance_low, y = tolerance_high, color = param, shape = setmember)
# ) + 
#   geom_point(size = 5, show.legend = TRUE) +
#   scale_shape_manual(values = setmember_shapes[14:27]) +
#   labs(
#     title = "Local Sensitivity Parameter Tolerance", 
#     color = "Parameter"
#   ) +
#   scale_x_log10(
#     name = "Tolerance Range Low End (as fraction of default value)", 
#     lim = c(0.8,1)
#   ) + 
#   scale_y_log10(
#     name = "Tolerance Range High End (as fraction of default value)", 
#     lim = c(1, 1.2)
#   ) +
#   geom_hline(yintercept = 1.1, color = "grey", lty = 2) + 
#   geom_vline(xintercept = 0.9, color = "grey", lty = 2) +
#   annotate("text", x = 1, y = 1.07, label = "Highly Sensitive") +
#   annotate("text", x = 0.8, y = 1, label = "Sensitive to Higher Values") +
#   annotate("text", x = 1, y = 1.2, label = "Sensitive to Lower Values") +
#   annotate("text", x = 0.8, y = 1.2, label = "Not Sensitive") +
#   facet_wrap("param_source") +
#   scale_color_manual(values = mycolors)
# 
# ggsave(
#   plot = tolerance.zoom, 
#   filename = paste0(figureoutputs, "ToleranceRanges_zoomed.png"), 
#   width = 16,
#   height = 10,
#   units = "in",
#   limitsize = FALSE
# )
```



## Save output
```{r write output}
write_csv(tolerance.ranges, file = paste0(figureoutputs, "ToleranceRanges.csv"))

write_csv(
  tolerance.ranges %>%
    filter(param_source == "User Supplied") %>%
    select(param, setmember, lowendtolerance, highendtolerance) %>%
    rename(
      Parameter = param, 
      `Set member (BMP or other)` = setmember,
      `Tolerance to decreased values` = lowendtolerance,
      `Tolerance to increased values` = highendtolerance
    ),
  file = paste0(figureoutputs, "UserGuide_table5-1.csv")
)

write_csv(
  tolerance.ranges %>%
    filter(param_source == "Provided Data") %>%
    select(param, setmember, lowendtolerance, highendtolerance) %>%
    rename(
      Parameter = param, 
      `Set member (BMP or other)` = setmember,
      `Tolerance to decreased values` = lowendtolerance,
      `Tolerance to increased values` = highendtolerance
    ),
  file = paste0(figureoutputs, "UserGuide_table5-2.csv")
)

ggsave(
  plot = cost.sens,
  filename = paste0(figureoutputs, "Fig3a.pdf"),
  width = 6,
  height = 6,
  units = "in",
  limitsize = FALSE,
  useDingbats = FALSE
)

ggsave(
  plot = space.sens,
  filename = paste0(figureoutputs, "Fig3b.pdf"),
  width = 6,
  height = 3,
  units = "in",
  limitsize = FALSE,
  useDingbats = FALSE
)
```

## Fit model curves to the loads_lim_N1 parameter sensitivity
```{r}

loads_lim_N1model <- with(
  all.costs %>% filter(param == "loads_lim_N1"), lm(cost_sens ~ log(frac))
)

bee <- all.costs %>% 
  filter(
    # param_source == "Provided Data",
    param %in% c(
      "loads_lim_N1"
    )
  )%>%
  ungroup() %>%
  group_by(param, frac) %>%
  summarize(cost_sens = mean(cost_sens)) %>%
  ungroup() # %>%
# add_row(
#   param = "loads_lim_N1",
#   frac = c(1.006, 1.007, 1.008, 1.009), 
#   cost_sens = exp(exp(predict.lm(
#     loads_lim_N1model, data.frame(frac = c(1.006, 1.007, 1.008, 1.009)
#     ))
#   ))
# )

ggplot(bee, aes(x = frac, y = cost_sens)) + 
  geom_point() + 
  scale_x_continuous(trans = "logit")
```

